---
title: "ECO 395M: Exercises 1"
author: "Haokun Zhang"
date: '2023-01-25'
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(rsample)  # for creating train/test splits
library(caret)
library(modelr)
library(parallel)
library(foreach)
library(stargazer)
library(knitr)

```

# 1) Data visualization: flights at ABIA

Your task is to create a figure, or set of related figures, that tell an interesting story about flights into and out of Austin.

```{r import and manipulate data, echo=FALSE}
ABIA = read.csv("../data/ABIA.csv")

#average delay time based on airtime
AVG_Delay <- aggregate(DepDelay ~ AirTime, ABIA, mean)
```

```{r airtime and delay, echo=FALSE}

ggplot(AVG_Delay, aes(x=AirTime, y=DepDelay))+
  geom_line()+
  ggtitle("Average Depature Delay based on Air Time")+
  labs(y= "Depature Delay (minutes)", x = "Air Time (minutes)")
```

The graph shows that average time of departure delays are similar to each other and slightly above 0 when the time of flight is between 50 to 200 minutes. When it exceeds 200 minutes, the average length of delay became larger and more volatile. When the air time is 281 minutes, the average departure delay is 413 minutes. 

# 2) Wrangling the Olympics

```{r load in data, echo=FALSE}
olympics_top20=read.csv("../data/olympics_top20.csv")

```


## A)  What is the 95th percentile of heights for female competitors across all Athletics events (i.e., track and field)? Note that `sport` is the broad sport (e.g. Athletics) whereas `event` is the specific event (e.g. 100 meter sprint).\
```{r data processing and table1, echo=FALSE, results='asis'}

olympics_female<-olympics_top20 %>%
  filter(sex =="F", sport=='Athletics') # filter female athletics

df <- data.frame(quantile = '95%', height = quantile(olympics_top20$height, probs=0.95), stringsAsFactors=FALSE)

kable(df, caption = '95% heights for female competitors')

```



## B)  Which single women's `event` had the greatest variability in competitor's heights across the entire history of the Olympics, as measured by the standard deviation?\
```{r table2, echo=FALSE}

#Filter by female
olympics_female<-olympics_top20 %>%
  filter(sex =="F")

#produce a sorted dataframe containing event and std dev
result<-split(olympics_female, olympics_female$event)%>%
  lapply(., function(x)sd(x$height))%>%
  unlist(.)%>%as.data.frame(.)
res<-cbind(row.names(result),result)
colnames(res)<-c("event","height_std_dev")

#sort by std_dev
res5 <- data.frame(head(res[order(res$height_std_dev, decreasing = TRUE),]))

kable(res5, caption = 'Top 5 Female Events that Have the Greatest Variability in Height')

```
The Rowing Women’s Coxed Fours had the greatest variability in competitor's heights across the entire history of the Olympics, as measured by the standard deviation. 

## C)  How has the average age of Olympic swimmers changed over time? Does the trend look different for male swimmers relative to female swimmers? Create a data frame that can allow you to visualize these trends over time, then plot the data with a line graph with separate lines for male and female competitors. Give the plot an informative caption answering the two questions just posed.

```{r age_graph, echo=FALSE}
olympics_swimmer <- olympics_top20 %>%
  filter(sport == 'Swimming')

#average age of swimmers over time
AVG_Age_Swimmer <- aggregate(age ~ year, olympics_swimmer, mean)

#average age of swimmers in different genders over time
AVG_Age_Gender <- aggregate(age ~ year + sex, olympics_swimmer, mean)

# linear graph
ggplot()+
  geom_line(data = AVG_Age_Swimmer, aes(x=year, y=age))+
  geom_smooth(span = 1)+
  geom_line(data=AVG_Age_Gender, aes(x=year, y=age, color = sex))

```


# 3) K-nearest neighbors: cars
The data in [sclass.csv](../data/sclass.csv) contains data on over 29,000 Mercedes S Class vehicles---essentially every such car in this class that was advertised on the secondary automobile market during 2014. For websites like Cars.com or Truecar that aim to provide market-based pricing information to consumers, the Mercedes S class is a notoriously difficult case. There is a huge range of sub-models that are all labeled "S Class,"" from large luxury sedans to high-performance sports cars; one sub-category of S class has even served as the safety car in Formula 1 Races. Moreover, individual submodels involve cars with many different features. This extreme diversity---unusual for a single model of car---makes it difficult to provide accurate pricing predictions to consumers.

Use K-nearest neighbors to build a predictive model for price, given mileage, separately for each of two trim levels: 350 and 65 AMG. That is, Treating the 350's and the 65 AMG's as two separate data sets.

```{r load_data, echo=FALSE}

sclass = read.csv('../data/sclass.csv')

trim_350 <- sclass %>%
  filter(trim =='350') #filter 350
trim_65_AMG <- sclass %>%
  filter(trim == '65 AMG') #filter AMG

# split testing and training dataset
trim_350_split =  initial_split(trim_350, prop=0.8)
trim350_train = training(trim_350_split)
trim350_test  = testing(trim_350_split)
trim_AMG_split = initial_split(trim_65_AMG, prop=0.8)
trimAMG_train = training(trim_AMG_split)
trimAMG_test = testing(trim_AMG_split)

# k-value cross validation
k_folds = 5

trim350_folds = crossv_kfold(trim_350, k=k_folds)
trimAMG_folds = crossv_kfold(trim_65_AMG,k=k_folds)

# define a series of k
k_grid = c(2, 4, 6, 8, 10, 15, 20, 25, 30, 35, 40, 45,
           50, 60, 70, 80, 90, 100, 125, 150, 175, 200, 250, 300)
```

## Trim 350
### KNN Test Plot
```{r trim350 knn plot, echo=FALSE, warning=FALSE}
cv_grid350 = foreach(k = k_grid, .combine='rbind') %dopar% {
  # map the model-fitting function over the training sets
  models = map(trim350_folds$train, ~ knnreg(price ~ mileage, k=k, data = ., use.all=FALSE))
  # map the RMSE calculation over the trained models and test sets simultaneously
  errs = map2_dbl(models, trim350_folds$test, modelr::rmse)
  c(k=k, err = mean(errs), std_err = sd(errs)/sqrt(k_folds)) # approximate standard error of CV error
} %>% as.data.frame

# plot means and std errors versus k
ggplot(cv_grid350) + 
  geom_point(aes(x=k, y=err)) + 
  geom_errorbar(aes(x=k, ymin = err-std_err, ymax = err+std_err)) + 
  scale_x_log10()
```

### Trim 350 Prediction Plot
```{r trim350 prediction, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# knn to 350
knn15 = knnreg(price ~ mileage, data=trim350_train, k=30)
modelr::rmse(knn15, trim350_test)

# attach the predictions to the test data frame
trim350_test = trim350_test %>%
  mutate(Price_pred = predict(knn15, trim350_test))

p_test = ggplot(data = trim350_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)

# add the predictions
p_test + geom_line(aes(x = mileage, y = Price_pred), color='red', size=1.5)
```

## Trim 65 AMG

### Trim 65 AMG KNN Test Plot
```{r TrimAMG knn plot, echo=FALSE, warning=FALSE}
cv_gridAMG = foreach(k = k_grid, .combine='rbind') %dopar% {
  # map the model-fitting function over the training sets
  models = map(trimAMG_folds$train, ~ knnreg(price ~ mileage, k=k, data = ., use.all=FALSE))
  # map the RMSE calculation over the trained models and test sets simultaneously
  errs = map2_dbl(models, trimAMG_folds$test, modelr::rmse)
  c(k=k, err = mean(errs), std_err = sd(errs)/sqrt(k_folds)) # approximate standard error of CV error
} %>% as.data.frame

# plot means and std errors versus k
ggplot(cv_gridAMG) + 
  geom_point(aes(x=k, y=err)) + 
  geom_errorbar(aes(x=k, ymin = err-std_err, ymax = err+std_err)) + 
  scale_x_log10()
```

### Trim 65 AMG Prediction Plot
```{r trimAMG Prediction Plot, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# knn to AMG
knn30 = knnreg(price ~ mileage, data=trim350_train, k=30)
modelr::rmse(knn30, trimAMG_test)

# attach the predictions to the test data frame
trimAMG_test = trimAMG_test %>%
  mutate(Price_pred = predict(knn30, trimAMG_test))

p_test = ggplot(data = trimAMG_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)

# add the predictions
p_test + geom_line(aes(x = mileage, y = Price_pred), color='red', size=1.5)
```

