---
title: "ECO 395M Homework 3"
author: "Haokun Zhang (hz7297), Jyun-Yu Cheng (jc95272) and Lu Zhang (lz7445) "
date: '2023-03-22'
output: 
  pdf_document: default
  md_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Loaded the needed packages
library(tidyverse)
library(ggplot2)
library(rsample)
library(modelr)
library(randomForest)
library(caret)
library(gbm)
library(ggmap)
library(glmnet)
library(rpart) # a powerful ML library that is used for building classification and regression trees
library(gamlr)
library(rpart.plot)
library(data.table)
library(DMwR2)
```

## What causes what?

1. The number of cops in the city doesn't direct cause the reduction of crime rate on streets. There are many other factors and events that have correlation to crime rates, such as terror alert level, and certain events and festivals that increase the number of cops deplied. Also, high crime rate in one area will naturally increase the cop forces deployed, thus will reduce the criminal rate. Focus only on the relationship between numbers of cops on the street and crime rate will lead to a endogeneity biased conclusion on causation of numbers of cops to the crime.

2. The researchers used daily police reports of crime from the Metropolitan Police Department of the District of Columbia that cover the time period of 506 days since the HSAS terror alert system began. During high alert level, the D.C. police forces increased their presence on the streets.The researchers used the high-alert periods to estimate the effect of police on crime and break the circle of endogenous relationship between police presence and crime rate. In Table 2, the daily total number of crimes in D.C. decreased by an average of seven crimes per day on high-alert days. 

3. The researchers included metro ridership as a variable to test their hypothesize that tourism is reduced on high-alert days, therefore there are less crimes on street. They added logged midday Metro ridership to the regression and captured the percentage of change on number of crimes based on the change of Metro ridership

4. Table 4 presents reduction in crime on high-alert days using police patrol concentration on hte national mall. The first column presents robust coefficient of estimation of crime in the National Mall area and the other districts during periods of high alert. 2.62 crimes decreased in the National Mall area, implying 15 percent of decline during high-alert days. Crime also decreases in the other districts, though the effect is not statistically significant. Lastly, ten percentage of increase on midday ridership increases 0.24 percent of crime rate.

## Question 2 : Tree modeling: dengue cases

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Read the dataset
dengue_fever <- read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/dengue.csv")
head(dengue_fever)

# Use KNN to impute the n.a. value
dengue_fever$total_cases <- as.numeric(as.character(dengue_fever$total_cases))
dengue_fever$city <- as.factor(dengue_fever$city)
dengue_fever$season <- as.factor(dengue_fever$season)
imputeDengue <- knnImputation(dengue_fever, k = 10, scale = T, meth = "median", distData = NULL)
head(imputeDengue)

# Split the dataset into training set and testing set
imputeDengue = initial_split(imputeDengue, prop = 0.8) # 80% of the data as training data
dengue_training = training(imputeDengue)
dengue_testing = testing(imputeDengue)
```

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# PART 2: Model building 

# CART model building
cart_dengue = rpart(total_cases ~ . , data = dengue_training, 
                  control = rpart.control(cp = 0.002, minsplit=20))
### Split only if we have at least 20 obs in a node,
### and the split improves the fit by a factor of 0.002 aka 0.2%

# Random Forest model building
## in the "random_forest_example.R"
rforest_dengue = randomForest(total_cases ~ .,
                             data = dengue_training, 
                             importance=TRUE)

# Gradient-boosted model building
## in the "capmetro.R"
gbm_dengue = gbm(total_cases ~ .,
                   data = dengue_training, 
                   interaction.depth=4, n.trees=500, shrinkage=.05)
```

Predict the dengue cases with CART model, Random Forest model and Gradient-boosted model
```{r,echo=FALSE, message= FALSE, warning=FALSE}
# PART 3: Use the models to Predict the infection cases, and find the model has the best performance
yhat_cart = predict(cart_dengue, dengue_testing)
plot(yhat_cart, dengue_testing$total_cases)
rmse(cart_dengue, dengue_testing)

yhat_rf = predict(rforest_dengue, dengue_testing)
plot(yhat_rf, dengue_testing$total_cases)
rmse(rforest_dengue, dengue_testing)

yhat_gbm = predict(gbm_dengue, dengue_testing, n.trees=350)
plot(yhat_gbm, dengue_testing$total_cases)
rmse(gbm_dengue, dengue_testing)
```


let's compare RMSE on the test set
```{r, echo=FALSE, message= FALSE, warning=FALSE}
modelr::rmse(cart_dengue, dengue_testing)
modelr::rmse(rforest_dengue, dengue_testing) 
modelr::rmse(gbm_dengue, dengue_testing) 
```

A K-fold test is conducted to further evaluate the performance
```{r,echo=FALSE, message= FALSE, warning=FALSE}
# evaluate the performance of three models by k-folds
# Perform cross-validation
set.seed(123)
k <- 5
cart_cv <- rpart.control(cp = 0.01)
rf_cv <- list(mtry = sqrt(ncol(dengue_training)), replace = TRUE)
gb_cv <- list(n.trees = 1000, interaction.depth = 4, shrinkage = 0.01, cv.folds = k)

cart_cv_results <- rpart(total_cases ~ ., data = dengue_training, control = cart_cv)
rf_cv_results <- randomForest(total_cases ~ ., data = dengue_training, mtry = rf_cv$mtry, replace = rf_cv$replace)
gb_cv_results <- gbm(total_cases ~ ., data = dengue_training, n.trees = gb_cv$n.trees, interaction.depth = gb_cv$interaction.depth, shrinkage = gb_cv$shrinkage, cv.folds = gb_cv$cv.folds, verbose = FALSE)

# Evaluate the performance of each model
cart_performance <- predict(cart_cv_results, newdata = dengue_testing)
rf_performance <- predict(rf_cv_results, newdata = dengue_testing)
gb_performance <- predict(gb_cv_results, newdata = dengue_testing, n.trees = gb_cv$n.trees)

# Compare the performance of each model by measuring MSE
cart_accuracy <- mean((cart_performance - dengue_testing$total_cases)^2)
rf_accuracy <- mean((rf_performance - dengue_testing$total_cases)^2)
gb_accuracy <- mean((gb_performance - dengue_testing$total_cases)^2)

# print out the MSE of each model to console, the lower the better the model is 
cat("CART accuracy:", cart_accuracy, "\n")
cat("Random Forest accuracy:", rf_accuracy, "\n")
cat("Gradient Boosting accuracy:", gb_accuracy, "\n") # gradient boosting has the lowest MSE
```

Because the gradient-boosted model has the smallest out-of-sample RMSE and MSE, we decided to choose it as the model to make partial dependence plots.

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# PART 4: Partial dependence plots
# Make the partial dependence plots
## gbm partial plots are in the "capmetro.R"
##### partialPlot(gbm_dengue, dengue_testing, 'specific_humidity', las=1)

plot(gbm_dengue, 'specific_humidity', main = "Partial Dependence on specific humidity")
plot(gbm_dengue, 'precipitation_amt', main = "Partial Dependence on precipitation_amt")
plot(gbm_dengue, 'tdtr_k', main = "Partial Dependence on tdtr_k")
```

We choose "tdtr_k" to make a partial dependence plots because we think that if the DTR is bigger, it's more difficult for mosquito to live as a result, we want to know whether DTR affect the total dengue fever cases and we can see that it has big influence on the infection cases.